\section{Introduction}
\label{sec:intro}

%What data is supplied

%main areas of investigation
%What methods are used
% AIMS AND OBJECTIVES OF THE PROJECT
% Aims are what you want to achieve, while, objectives are what you will do to achieve them. An objective is more specific in character, while an aim is more abstract. Also, an objective is time-bound whereas an aim need not be.


% The use of GPS systems has grown exponentially over the last 15 years, both on a personal and commercial level. Therefore large stores of GPS data are readily available, from anything between a smart phone and a tracking device, and highly useful information can be extracted. The aims of this project are to define the typical behavioural patterns of GAStech employees and hence extract behaviours that do not follow the trend.\\
% \noindent The objectives are to use various data analysis techniques to find this anomalous behaviour, and to draw conclusions from these results to identify whether or not these anomalies are substantial. 

%objectives - 
%Aims - To find outliers in the data, 
Large stores of GPS data are now readily available, with the development of smart phones and tracking devices. From apps that suggest running routes to car insurance prices dependent of the quality of the driver stem from GPS data analysis, and it is an increasingly important field of research.  For this project data is given by GAStech in order to investigate the disappearance of several employees shortly after the public offering of shares of the company. The data available is only for the two weeks prior to the disappearance excluding the day in question.

\subsection{Aims and Objectives}

The aim of this project is to identify typical behaviour of GAStech employees and hence identify unsual patterns within the data, so suspects linked with disappearance can be identified. To do this, imperfections such as missing data, have to be rectified. Data regarding the spending from different accounts must also be utilized to find patterns. The difference between unusual patterns in the data and anomalies that bear no significance to the invistigation must also be established. 